Pillar 1 - Sequential Pattern Mining

### 2019-03-12 Pillar 1 - Sequential Pattern Mining.Rmd
Use tidyr::complete instead of expand.grid + join for simplicity

### Take / not take, pass / fail / not take
```{r d_transactions T_PF_HL}
d_transactions$T_PF_HL <- expand.grid(

  # Expand along students (sequenceID) and courses (itemID)
  sequenceID       = student_all,
  item             = course_all,
  stringsAsFactors = FALSE
  ) %>%

  # Join with d_transactions
  left_join(
    d_transactions$taken_PF_HL, 
    by = c("sequenceID", "item")
    ) %>%

  # Create item
  mutate(

    TPF = case_when(
      is.na(Grade)        ~ "not",
      Grade <  pass_grade ~ "fail",
      Grade >= pass_grade ~ "pass"
      ),
    THL = case_when(
      is.na(Grade)        ~ "not",
      Grade <  high_grade ~ "low",
      Grade >= high_grade ~ "high"
      ),

    item_TPF = paste(item, TPF, sep = "_"),

    item_THL = paste(item, THL, sep = "_")

>>>>

### Take / not take, pass / fail / not take
```{r d_transactions T_PF_HL}
d_transactions$T_PF_HL <- d_transactions$taken_PF_HL %>%

  # Expand along students (sequenceID) and courses (itemID) to make missing combinations of student - course explicit
  complete(sequenceID, item) %>%

  # create a new type of item: "not taken"
  mutate(
    item_TPF = if_else(is.na(item_PF), paste_(item, "not"), item_PF),
    item_THL = if_else(is.na(item_HL), paste_(item, "not"), item_HL)
    )
```
